---
title: "Extreme Temperature Risk for Wheat Crops"
author: "Genevieve Chiong"
date: "3/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

source(here("R/crop_temperature.R"))
```


```{r}
tmax <- read_delim(here("data", "tmax.txt"), delim = " ")
```


```{r}
# nsample_age = 7920
# mean_age = 4
# 
# age = rlnorm(mean = mean_age,
#              sd = 1,
#              nsample_age)

age = runif(min = 1, max = 12, n = 7920) 
```

```{r}
crop_temperature(daily_temp = tmax$tmax, age = age)
```


Generally, caution should be taken if the heat index is over 77 degrees (Fahrenheit). Above 82 degrees is considered 'extreme caution' — heat-related illness is possible with long exposure. Over 85 is dangerous — heat illness is likely and heat stroke is possible.

77 - low
80 - medium 
82 - extreme
85 + -- dangerous 


or impact on agriculture??? 

temperature, crop species, crop age, nutrient levels, irrigation 



